---
title: "Exercises 10.5"
author: "Tiffany Cheng"
date: "February 20, 2018"
output:
  word_document: default
  pdf_document: default
---

```{r,echo=FALSE}
# load library
library(tidyverse)
library(tibble)
```

## 1. How can you tell if an object is a tibble? (Hint: try printing `mtcars`, which is a regular data frame).
```{r}
print(mtcars)
class(mtcars)
```
When a tibble is printed to the console, it will only print the first 10 lines of the data and it will mention that it is of class `tibble` and each column will have the type of data stored in it, such as integer, factor, etc. Here, `mtcars` is a data frame because such labeling does not exist.

## 2. Compare and contrast the following operations on a `data.frame` and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x # returns the column with an "x" in it
df[, "xyz"] # returns a data frame with xyz as a factor
df[, c("abc", "xyz")] # returns a data frame

tib <- tibble(abc = 1, xyz = "a")
tib$x # returns nothing, does not do partial matching
tib[, "xyz"] # returns a tibble with xyz as a character
tib[, c("abc", "xyz")] # returns a tibble
```
These differences can cause frustration when there are column names that have the same words in it, but you only want to select a certain column.

## 3. If you have the name of a variable stored in an object, e.g. `var <- "mpg"`, how can you extract the reference variable from a tibble?
```{r}
var <- "xyz"
tib[[var]] # returns a vector
tib[var] # returns a tibble
```

## 4. Practice referring to non-syntactic names in the following data frame by:
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```

### 1. Extracting the variable called `1`.
```{r}
annoying$`1`
```

### 2. Plotting a scatterplot of `1` vs `2`.
```{r}
ggplot(data=annoying) + geom_point(mapping=aes(x=annoying$`1`,y=annoying$`2`))
```

### 3. Creating a new column called `3` which is `2` divided by `1`.
```{r}
annoying <- 
  annoying %>% mutate(`3`=`2`/`1`)
annoying
```

### 4. Renaming the columns to `one`, `two` and `three`.
```{r}
annoying <- 
  annoying %>% rename(one=`1`,two=`2`,three=`3`)
annoying
```

## 5. What does `tibble::enframe()` do? When might you use it?

`enframe()` converts vectors to tibbles and `deframe()` does the opposite. This can be used when you have a list and would like to turn it into a dataset.

## 6. What option controls how many additional column names are printed at the footer of a tibble?

`tibble.max_extra_cols` controls the additional column names printed at the footer of the tibble.
```{r}
options(tibble.max_extra_cols=2) # for example
```
